\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
% Max 3 pages

\begin{document}
\section{Matthew L. Curry, Ph.D.}

Matthew L. Curry is a Senior Member of Technical Staff at Sandia
National Laboratories. His primary areas of research include
extreme-scale file and storage systems, application of erasure coding
algorithms and other data safety algorithms to storage, heterogeneous
computing, and characteristics of low-level storage devices. He has
given invited lectures at EMC, the University of Alabama at
Birmingham, and Auburn University.

\subsection{Program Committees}
\begin{itemize}
\item The 7th Parallel Data Storage Workshop, held in conjunction with
  Supercomputing 2012.
\item The 28th IEEE Conference on Massive Data Storage (MSST 2012)
\item The 4th International Workshop on Frontiers of Heterogeneous
  Computing (FHC 2013)
\end{itemize}

\subsection{Reviewing Activities}
He performs several reviews a year for the following journals:
\begin{itemize}
\item ACM Transactions on Storage
\item ACM Transactions on Parallel Computing
\item Concurrency and Computation, Practice and Experience
\end{itemize}

\subsection{Education and Training}
\begin{itemize}
\item Ph.D., Computer and Information Sciences\\ University of Alabama at Birmingham, December 2010
\item M.S., Computer and Information Sciences\\ University of Alabama at Birmingham, May 2008
\item B.S., Computer and Information Sciences\\ University of Alabama at Birmingham, December 2004
\end{itemize}

\subsection{Research and Professional Experience}
\begin{itemize}
\item {\bf Senior Member of Technical Staff, Scalable System Software,
  Sandia National Laboratories}, 2010-Present.\\ Performing research
  and development activities associated with high-performance storage
  and operating systems for massively parallel computing systems.
\item {\bf Systems Analyst, Department of Computer and Information
  Sciences, University of Alabama at Birmingham}, January 2009 - May
  2009.\\ Supported research software development activities for NSF
  Award CNS-0821497, ``MRI: Development of a GPU-Enabled Integrated
  Storage Computation Architecture and System.''
\item {\bf Student Intern, Sandia National Laboratories}, Summers
  2005-2008 and May 2009-December 2010.\\ Performed research and
  development activities associated with high-performance storage and
  operating systems for massively parallel computing systems.
\item {\bf Teaching and Research Assistant, Department of Computer and
  Information Sciences, University of Alabama at Birmingham}, during
  spring and fall semesters beginning January 2005 and ending May
  2009.\\ Performed research, taught courses (Operating Systems,
  Introduction to C++), gave guest lectures (Parallel Computing,
  Software Engineering), graded, and conducted labs.
\end{itemize}

\subsection{Publications}

\begin{enumerate}
\item {\sl Gibraltar: A Reed-Solomon Coding Library for Storage Applications
  on Programmable Graphics Processors}.  Matthew L. Curry, Anthony
Skjellum, H. Lee Ward, Ron Brightwell (2011). Concurrency and
Computation, Practice and Experience, Volume 23, Issue 18 (pages
2477-2495).
\item {\sl GPUstore: Harnessing GPU Computing for Storage Systems in
  the OS Kernel}. Weibin Sun, Robert Ricci, Matthew L Curry. The 5th
  Annual International Systems and Storage Conference (SYSTOR 2012).
\item {\sl A Lightweight, GPU-Based Software RAID System}. Matthew
  L. Curry, H. Lee Ward, Anthony Skjellum, Ron
  Brightwell. International Conference on Parallel Processing (ICPP)
  2010.
\item {\sl Accelerating Reed-Solomon coding in RAID systems with
  GPUs}. Matthew L. Curry, Anthony Skjellum, H. Lee Ward, Ron
  Brightwell. IEEE International Parallel and Distributed Processing
  Symposium (IPDPS) 2008.
\item {\sl Power Use of Disk Subsystems in Supercomputers}.  Matthew
  L. Curry, H. Lee Ward, Gary Grider, Jill Gemmill, Jay Harris, David
  Martinez (2011). Proceedings, 6th Parallel Data Storage Workshop,
  Seattle, Washington.
\item {\sl Failing in Place for Low-Serviceability Infrastructure
  Using High-Parity GPU-Based RAID}. Matthew L. Curry, H. Lee Ward,
  Anthony Skjellum, High Performance Embedded Computing Workshop
  (HPEC) 2010.
\item {\sl Using GPUs to Enable Highly Reliable Embedded Storage}.
  Matthew L. Curry, Anthony Skjellum, Lee Ward, Ron Brightwell. HPEC
  2008. September 24, 2008.
\item {\sl Arbitrary Dimension Reed-Solomon Coding and Decoding for
  Extended RAID on GPUs}.  Matthew L. Curry, H. Lee Ward, Anthony
  Skjellum, Ron Brightwell. 3rd Petascale Data Storage Workshop held
  in conjunction with SC08, Austin, TX. Nov. 17, 2008.
\item {\sl Using the Sirocco File System for High-Bandwidth
  Checkpoints}. Matthew L. Curry, Ruth Klundt, H. Lee Ward. Technical
  Report. SAND2012-1087.
\item {\sl A Highly Reliable GPU-based RAID System}. Matthew
  L. Curry. Doctoral thesis, University of Alabama at Birmingham,
  2010, 141 pages. Available online:
  \url{http://www.mhsl.uab.edu/dt/2010p/curry.pdf}.
\end{enumerate}


\subsection{Synergistic Activities}
\begin{itemize}
\item Member of the Board of Directors for the New Mexico Supercomputing Challenge (\url{http://www.supercomputingchallenge.org/about/}.
\item Sandia POC for the DOE Storage Fast-Forward 2 effort.
\end{itemize}
\subsection{Identification of Potential Conflicts of Interest or Bias in Selection of Reviewers}
\begin{itemize}
\item Purushotham V. Bangalore; University of Alabama at Birmingham (collaborator)
\item Ron Brightwell; Sandia National Laboratories (co-author, collaborator)
\item Phil Carns; Argonne National Laboratory (co-author, collaborator)
\item Geoff Danielson; Sandia National Laboratories (collaborator)
\item Jill Gemmill; Clemson University (co-author)
\item Kevin Harms; Argonne National Laboratory (co-author)
\item Jay Harris; Clemson University (co-author)
\item Dries Kimpe; Argonne National Laboratory (co-author, collaborator)
\item Ruth Klundt; Sandia National Laboratories (co-author)
\item Thomas Kroeger; Sandia National Laboratories (collaborator)
\item Darrell Long; University of California-Santa Cruz (collaborator)
\item Carlos Maltzahn; University of California-Santa Cruz (co-author, collaborator)
\item Ethan Miller; University of California-Santa Cruz (collaborator)
\item Ron Oldfield; Sandia National Laboratories (collaborator)
\item David R. Resnick; Sandia National Laboratories (co-author)
\item Robert Ricci; University of Utah (co-author)
\item Robert Ross; Argonne National Laboratory (co-author, collaborator)
\item Haiying Shen; Clemson University (collaborator)
\item Anthony Skjellum; Auburn University (co-author, collaborator, Ph.D. advisor)
\item Weibin Sun; Google (co-author)
\item Zhiwei Sun; Data Direct Networks (co-author, collaborator)
\item Lee Ward; Sandia National Laboratories (co-author, collaborator)
\end{itemize}

\end{document}
