\documentclass[11pt]{article}
%\usepackage[utf8]{inputenc}
\usepackage[margin=1.0in]{geometry}
%opening
\title{Mark Ainsworth}
\author{}
\date{}

\begin{document}

\maketitle

\flushleft{\sc\bf Professional Preparation}
       PhD Mathematics (1989). Durham University, UK. 1986-1989;
       BSc (Hons) Mathematics, {\em First class.} Durham University,
       UK. 1983-1986.

\flushleft{\bf Selected Appointments and Honours}
     2012-Present \emph{Professor of Applied Mathematics}, Brown
         University;
     2004-2012 \emph{The 1825 Chair Professor of Mathematics},
         Strathclyde University, UK;
     1998-2004 \emph{Professor of Applied Mathematics}, Strathclyde
         University, UK;
	 \emph{LMS Whitehead Prize (London Math Society)},  
	 \emph{J.L. Lions Prize for Computational Mathematics},
	 \emph{SIAM Fellow},
	 \emph{Fellow Royal Society of Edinburgh},
	 \emph{Fellow Inst. Math. Applic.}.

  \nocite{Ainsworth+Andriamaro+etal:Bernstein-Bezier}
  \nocite{Ainsworth+Rankin:Guaranteed}
  \nocite{Ainsworth:synthesis}
  \nocite{Ainsworth+Oden:book}
  \nocite{Ainsworth+Rankin:Robust}
  \nocite{Ainsworth+Rankin:Quantities}
  \nocite{Ainsworth+Ma:Non-uniform}
  \nocite{Ainsworth+Vejchodsky:Fully}
  \nocite{Ainsworth+Senior:Aspects}
  \nocite{Ainsworth:framework}
  
  
\flushleft{\bf Synergistic Activities}
        Director of NAIS, 2010-2012. NAIS is a UK based research
            centre supported by \pounds 4.5M from EPSRC under contract
            EP/G036136/1 {\em Numerical Algorithms and Intelligent Software
            for the Evolving HPC Platform}. 
        Organiser of meeting on {\em Scientific Computing at the
            Exascale}, 11th October 2011, London sponsored by London
            Mathematical Society;
        Membership of over 10 editorial boards including {\em SIAM Journal on Scientific
            Computing} (2001-present) {\em SIAM Journal on Numerical Analysis}
            (2012-present);
        Chair of {\em Biennial Conference on Numerical Analysis} held
            at Strathclyde University, June 2011, June 2013;
	Plenary speaker at {\em ENUMATH European Conference on Numerical Mathematics},
            September 2015, Turkey. 

\renewcommand{\refname}{\small\bf Selected Recent Publications}
%\bibliography{$HOME/Research/Papers/tools/mybib}
%\bibliographystyle{siam}
\begin{thebibliography}{10}

\bibitem{Ainsworth:synthesis}
{\sc M.~Ainsworth}, {\em A synthesis of a posteriori error estimation
  techniques for conforming, non-conforming and discontinuous {G}alerkin finite
  element methods}, Contemp. Math., 383 (2005), pp.~1--14.

\bibitem{Ainsworth:framework}
\leavevmode\vrule height 2pt depth -1.6pt width 23pt, {\em A framework for
  obtaining guaranteed error bounds for finite element approximations}, J.
  Comput. Appl. Math., 234 (2010), pp.~2618 -- 2632.

\bibitem{Ainsworth+Andriamaro+etal:Bernstein-Bezier}
{\sc M.~Ainsworth, G.~Andriamaro, and O.~Davydov}, {\em Bernstein-{B}\'ezier
  {FEM} and optimal assembly algorithms}, SIAM J. Sci. Comp.,  (2011),
  pp.~3087--3109.

\bibitem{Ainsworth+Ma:Non-uniform}
{\sc M.~Ainsworth and X.~Ma}, {\em Non-uniform order mixed {FEM} approximation:
  implementation, post-processing, computable error bound and adaptivity}, J.
  Comput. Phys., 231 (2012), pp.~436--453.

\bibitem{Ainsworth+Oden:book}
{\sc M.~Ainsworth and J.~Oden}, {\em A posteriori error estimation in finite
  element analysis}, Pure and Applied Mathematics, Wiley-Interscience, John
  Wiley \& Sons, New York, 2000.

\bibitem{Ainsworth+Rankin:Robust}
{\sc M.~Ainsworth and R.~Rankin}, {\em Robust a posteriori error estimation for
  the nonconforming {F}ortin-{S}oulie finite element approximation}, Math.
  Comp., 77 (2008), pp.~1917--1939.

\bibitem{Ainsworth+Rankin:Guaranteed}
\leavevmode\vrule height 2pt depth -1.6pt width 23pt, {\em Guaranteed
  computable error bounds for conforming and nonconforming finite element
  analyses in planar elasticity}, Internat. J. Numer. Methods Engrg., 82
  (2010), pp.~1114--1157.

\bibitem{Ainsworth+Rankin:Quantities}
\leavevmode\vrule height 2pt depth -1.6pt width 23pt, {\em Guaranteed
  computable bounds on quantities of interest in finite element computations},
  Internat. J. Numer. Methods Engrg., 89 (2012), pp.~1605--1634.

\bibitem{Ainsworth+Senior:Aspects}
{\sc M.~Ainsworth and B.~Senior}, {\em Aspects of an adaptive $hp$-finite
  element method: Adaptive strategy, conforming approximation and efficient
  solvers}, Comput. Methods Appl. Mech. Engrg., 150 (1997), pp.~65--87.

\bibitem{Ainsworth+Vejchodsky:Fully}
{\sc M.~Ainsworth and T.~Vejchodsk{\'y}}, {\em Fully computable robust a
  posteriori error bounds for singularly perturbed reaction-diffusion
  problems}, Numer. Math., 119 (2011), pp.~219--243.

\end{thebibliography}


\flushleft{\bf Recent Collaborators and Co-Editors}
Allendes, Alejandro (Universidad T\'ecnica Federico Santa
Mar\'ia, Chile); 
Andriamaro, Gaelle (Strathclyde University, UK); 
Barrenechea, Gabriel R. (Strathclyde University, UK); 
Davydov, Oleg (Giessen University, Germany); 
Guzman, Johnny (Brown University); 
Karniadakis, George (Brown University); 
Ma, Xinhui (Abertay University, UK); 
Mihai, L. Angela (Cardiff University, UK); 
Rankin, Richard (Rice University, US); 
Sayas, Francisco-Javier (University of Delaware); 
Wajid, Hafiz Abdul (COMSATS Institute of Technology, Pakistan).

\flushleft{\bf Graduate and Postdoctoral Advisors and Advisees}
Graduate Advisor: Craig, Alan W. (European Commission, Brussels); Post-doctoral
Advisor: Oden, John T. (University of Texas at Austin, US); Graduate and
Postdoctoral Advisors and Advisees: Allendes, Alejandro (Universidad T\'ecnica
Federico Santa Mar\'ia, Chile); Andriamaro, Gaelle (Strathclyde University, UK);
Ma, Xinhui (Abertay University, UK); Mihai, L. Angela (Cardiff University, UK);
Rankin, Richard (Rice University, US); Wajid, Hafiz Abdul (COMSATS Institute of
Technology, Pakistan).
\end{document}
