\documentclass[11pt]{nsfcv}

%\newcommand{\elm}{E.~L. Miller}
%\newcommand{\exm}{E.~Miller}
%\newcommand{\person}[5]{\item #2, #1: #3 #4 (#5);\xspace}

\begin{document}
\begin{center}
  {\bf\Large Lee Ward} \\
  {\bf\Large Principal Member of Technical Staff} \\
  Sandia National Laboratories \\
  Phone: +1 (505) 844-9545 \\
  Email: \verb+lee@sandia.gov+
\end{center}

%\section*{Education}
%\begin{yearlist}
%\item[1995] Ph.\,D. (computer science), University of California at Berkeley
%\item[1990] M.\,S. (computer science), University of California at Berkeley
%\item[1987] Sc.\,B. (computer science), Brown University
%\end{yearlist}

\section*{Professional Experience}
\begin{yearlist}

\item[2000--\hfill]
  Principal Member of Technical Staff, Sandia National Laboratories. Conduct research
  on high performance file systems and storage.

\end{yearlist}

\section*{Qualifications Summary}

\begin{itemtight}
\item Designed and wrote the eNFS filel system service for Sandia's CPlant clusters
\item Designed and wrote the libsysio virtual file system interface for Cray-XT class
  machines running the Catamount operating system
\item Received two patents for error correcting codes applicable to 3D stacked-silicon memories
\end{itemtight}

\section*{Selected Recent Publications}
\begin{publist}

\item
  Liu, Guoxin, Haiying Shen, and Lee Ward.
  ``An efficient and trustworthy P2P and social network integrated file sharing system.'' Computers, IEEE Transactions on 64, no. 1 (2015): 54-70.

\item
  Karakoyunlu, Cengiz, Dries Kimpe, Philip Carns, Kevin Harms, Robert Ross, and Lee Ward.
  ``Toward a unified object storage foundation for scalable storage systems.''
  In Cluster Computing (CLUSTER), 2013 IEEE International Conference on, pp. 1-8. IEEE, 2013.

\item
  Carns, Philip, Kevin Harms, Dries Kimpe, Justin M. Wozniak, Robert Ross, Lee Ward, Matthew Curry et al.
  ``A case for optimistic coordination in hpc storage systems.'' In High Performance Computing, Networking, Storage and Analysis (SCC), 2012 SC Companion:, pp. 48-53. IEEE, 2012.

\item
  Wildani, Avani, Ethan L. Miller, and Lee Ward.
  ``Efficiently identifying working sets in block i/o streams."
  In Proceedings of the 4th Annual International Conference on Systems and Storage, p. 5. ACM, 2011.

\item
  Curry, Matthew L., Anthony Skjellum, H. Lee Ward, and Ron Brightwell.
  ``Gibraltar: A Reed‐Solomon coding library for storage applications on programmable graphics processors.'' Concurrency and Computation: Practice and Experience 23, no. 18 (2011): 2477-2495.

\end{publist}

\newpage
\section*{Conflicts of Interest}

\subsection*{Collaborators and Co-authors (in past 48 months)}
\begin{itemtight}
\item Arpaci-Dusseau, Remzi  (University of Wisconsin - Madison): collaborator
\item Brooks, Richard (Clemson University): collaborator
\item Carns, Phil (Argonne National Laboratory): co-author; collaborator
\item Harms, Kevin (Argonne National Laboratory): co-author
\item Kelly, Suzanne (Sandia National Laboratories): co-author
\item Kimpe, Dries (Argonne National Laboratory): co-author
\item Reddy, Narasimha (Texas A\&M University): co-author; collaborator
\item Resnick, David (Sandia National Laboratory): co-author
\item Ross, Robert (Argonne National Laboratory): co-author; collaborator
\item Shen, Haiying (Clemson University): co-author; collaborator
\item Skjellum, Anthony (Auburn University): co-author; collaborator
\item Sun, Zhiwei (Data Direct Networks): co-author
\item Long, Darrell (University of California, Santa Cruz); co-author, collaborator
\item Miller, Ethan (University of California, Santa Cruz); co-author, collaborator
\end{itemtight}

\end{document}
