\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{times}
\setlist{nolistsep} % Makes itemize tighter
% Max 3 pages

\begin{document}
\title{Matthew L. Curry, Ph.D.}
\author{}
\date{}
\maketitle
\vspace{-0.75in}
Matthew L. Curry is a Senior Member of Technical Staff at Sandia
National Laboratories. His primary areas of research include
extreme-scale file and storage systems, application of erasure coding
algorithms and other data safety algorithms to storage, heterogeneous
computing, and characteristics of low-level storage devices. He has
given invited lectures at EMC, the University of Alabama at
Birmingham, and Auburn University.

\vspace{-0.75em}
\section*{Program Committees}
\vspace{-0.75em}
\begin{itemize}
\item The 7th Parallel Data Storage Workshop, held in conjunction with
  Supercomputing 2012.
\item The 28th IEEE Conference on Massive Data Storage (MSST 2012)
\item The 4th International Workshop on Frontiers of Heterogeneous
  Computing (FHC 2013)
\end{itemize}

\vspace{-0.75em}
\section*{Reviewing Activities}
\vspace{-0.75em}
He performs several reviews a year for the following journals:
\begin{itemize}
\item ACM Transactions on Storage
\item ACM Transactions on Parallel Computing
\item Concurrency and Computation, Practice and Experience
\end{itemize}

\vspace{-0.75em}
\section*{Education and Training}
\vspace{-0.75em}
%{\bf Undergraduate, graduate and postdoctoral training, provide institution, major/area, degree and year.}
\begin{itemize}
\item Ph.D., Computer and Information Sciences, University of Alabama at Birmingham, December 2010.
\item M.S., Computer and Information Sciences, University of Alabama at Birmingham, May 2008.
\item B.S., Computer and Information Sciences, University of Alabama at Birmingham, December 2004.
\end{itemize}

\vspace{-0.75em}
\section*{Research and Professional Experience}
\vspace{-0.75em}
%{\bf Beginning with the current position list, in re- verse chronological order, professional/academic positions with a brief description of responsibilities.}
\begin{itemize}
\item {\bf Senior Member of Technical Staff, Scalable System Software,
  Sandia National Laboratories}, 2010-Present. Performing research
  and development activities associated with high-performance storage
  and operating systems for massively parallel computing systems.
\item {\bf Systems Analyst, Department of Computer and Information
  Sciences, University of Alabama at Birmingham}, January 2009 - May
  2009. Supported research software development activities for NSF
  Award CNS-0821497, ``MRI: Development of a GPU-Enabled Integrated
  Storage Computation Architecture and System.''
\item {\bf Student Intern, Sandia National Laboratories}, Summers
  2005-2008 and May 2009-December 2010. Performed research and
  development activities associated with high-performance storage and
  operating systems for massively parallel computing systems.
\item {\bf Teaching and Research Assistant, Department of Computer and
  Information Sciences, University of Alabama at Birmingham}, during
  spring and fall semesters beginning January 2005 and ending May
  2009. Performed research, taught courses (Operating Systems,
  Introduction to C++), gave guest lectures (Parallel Computing,
  Software Engineering), graded, and conducted labs.
\end{itemize}

\vspace{-0.75em}
\section*{Publications}
\vspace{-0.75em}
%{\bf Provide a list of up to 10 publications most closely related to the proposed project. For each publication, identify the names of all authors (in the same sequence in which they appear in the publication), the article title, book or journal title, volume number, page numbers, year of publication, and website address if available electroni- cally. Patents, copyrights and software systems developed may be provided in addition to or substituted for publications. . An abbreviated style such as the Physical Re- view Letters (PRL) convention for citations (list only the first author) may be used for publications with more than 10 authors.}

\begin{enumerate}
\item {\sl Gibraltar: A Reed-Solomon Coding Library for Storage Applications
  on Programmable Graphics Processors}.  Matthew L. Curry, Anthony
Skjellum, H. Lee Ward, Ron Brightwell (2011). Concurrency and
Computation, Practice and Experience, Volume 23, Issue 18 (pages
2477-2495).
\item {\sl GPUstore: Harnessing GPU Computing for Storage Systems in
  the OS Kernel}. Weibin Sun, Robert Ricci, Matthew L Curry. The 5th
  Annual International Systems and Storage Conference (SYSTOR 2012).
\item {\sl A Lightweight, GPU-Based Software RAID System}. Matthew
  L. Curry, H. Lee Ward, Anthony Skjellum, Ron
  Brightwell. International Conference on Parallel Processing (ICPP)
  2010.
\item {\sl Accelerating Reed-Solomon coding in RAID systems with
  GPUs}. Matthew L. Curry, Anthony Skjellum, H. Lee Ward, Ron
  Brightwell. IEEE International Parallel and Distributed Processing
  Symposium (IPDPS) 2008.
\item {\sl Power Use of Disk Subsystems in Supercomputers}.  Matthew
  L. Curry, H. Lee Ward, Gary Grider, Jill Gemmill, Jay Harris, David
  Martinez (2011). Proceedings, 6th Parallel Data Storage Workshop,
  Seattle, Washington.
\item {\sl Failing in Place for Low-Serviceability Infrastructure
  Using High-Parity GPU-Based RAID}. Matthew L. Curry, H. Lee Ward,
  Anthony Skjellum, High Performance Embedded Computing Workshop
  (HPEC) 2010.
\item {\sl Using GPUs to Enable Highly Reliable Embedded Storage}.
  Matthew L. Curry, Anthony Skjellum, Lee Ward, Ron Brightwell. HPEC
  2008. September 24, 2008.
\item {\sl Arbitrary Dimension Reed-Solomon Coding and Decoding for
  Extended RAID on GPUs}.  Matthew L. Curry, H. Lee Ward, Anthony
  Skjellum, Ron Brightwell. 3rd Petascale Data Storage Workshop held
  in conjunction with SC08, Austin, TX. Nov. 17, 2008.
\item {\sl Using the Sirocco File System for High-Bandwidth
  Checkpoints}. Matthew L. Curry, Ruth Klundt, H. Lee Ward. Technical
  Report. SAND2012-1087.
\item {\sl A Highly Reliable GPU-based RAID System}. Matthew
  L. Curry. Doctoral thesis, University of Alabama at Birmingham,
  2010, 141 pages. Available online:
  \url{http://www.mhsl.uab.edu/dt/2010p/curry.pdf}.
\end{enumerate}


\vspace{-0.75em}
\section*{Synergistic Activities}
\vspace{-0.75em}
%{\bf List no more than 5 professional and scholarly activities related to the effort proposed.}
\begin{itemize}
\item Member of the Board of Directors for the New Mexico Supercomputing Challenge (\url{http://www.supercomputingchallenge.org/about/}.
\item Sandia POC for the DOE Storage Fast-Forward 2 effort.
\end{itemize}
\section*{Collaborators/Conflicts of Interest}
% This part can extend past the three pages
%\subsection*{Collaborators and Co-Editors}
% {\bf List in alphabetical order all persons, including their first and last names and current organizational affiliation, who are, or who have been, collaborators or co-authors with you on a research project, book or book article, report, abstract, or paper during the 48 months preceding the submission of this application. For publications or collaborations with more than 10 authors or participants, only list those individuals in the core group with whom the Principal Investigator interacted on a regular basis while the research was being done. Also, list any individuals who are currently, or have been, co-editors with you on a special issue of a journal, compendium, or conference proceedings during the 24 months preceding the submission of this application. For each COI, include the source of the conflict (e.g., co-author, collaborator, co-editor, graduate student, advisor). If there are no collaborators or co-editors to report, state None. The COI list may require additional pages beyond the three-page limit.}
\iffalse
\begin{itemize}
\item Purushotham V. Bangalore; University of Alabama at Birmingham (collaborator)
\item Ron Brightwell; Sandia National Laboratories (co-author, collaborator)
\item Phil Carns; Argonne National Laboratory (co-author, collaborator)
\item Geoff Danielson; Sandia National Laboratories (collaborator)
\item Jill Gemmill; Clemson University (co-author)
\item Kevin Harms; Argonne National Laboratory (co-author)
\item Jay Harris; Clemson University (co-author)
\item Dries Kimpe; Argonne National Laboratory (co-author, collaborator)
\item Ruth Klundt; Sandia National Laboratories (co-author)
\item Thomas Kroeger; Sandia National Laboratories (collaborator)
\item Darrell Long; University of California-Santa Cruz (collaborator)
\item Carlos Maltzahn; University of California-Santa Cruz (co-author, collaborator)
\item Ethan Miller; University of California-Santa Cruz (collaborator)
\item Ron Oldfield; Sandia National Laboratories (collaborator)
\item David R. Resnick; Sandia National Laboratories (co-author)
\item Robert Ricci; University of Utah (co-author)
\item Robert Ross; Argonne National Laboratory (co-author, collaborator)
\item Haiying Shen; Clemson University (collaborator)
\item Anthony Skjellum; Auburn University (co-author, collaborator, Ph.D. advisor)
\item Weibin Sun; Google (co-author)
\item Zhiwei Sun; Data Direct Networks (co-author, collaborator)
\item Lee Ward; Sandia National Laboratories (co-author, collaborator)
\end{itemize}
\fi
Purushotham V. Bangalore, University of Alabama at Birmingham (collaborator).
Ron Brightwell, Sandia National Laboratories (co-author, collaborator).
Phil Carns, Argonne National Laboratory (co-author, collaborator).
Geoff Danielson, Sandia National Laboratories (collaborator).
Jill Gemmill, Clemson University (co-author).
Kevin Harms, Argonne National Laboratory (co-author).
Jay Harris, Clemson University (co-author).
Dries Kimpe, Argonne National Laboratory (co-author, collaborator).
Ruth Klundt, Sandia National Laboratories (co-author).
Thomas Kroeger, Sandia National Laboratories (collaborator).
Darrell Long, University of California-Santa Cruz (collaborator).
Carlos Maltzahn, University of California-Santa Cruz (co-author, collaborator).
Ethan Miller, University of California-Santa Cruz (collaborator).
Ron Oldfield, Sandia National Laboratories (collaborator).
David R. Resnick, Sandia National Laboratories (co-author).
Robert Ricci, University of Utah (co-author).
Robert Ross, Argonne National Laboratory (co-author, collaborator).
Haiying Shen, Clemson University (collaborator).
Anthony Skjellum, Auburn University (co-author, collaborator, Ph.D. advisor).
Weibin Sun, Google (co-author).
Zhiwei Sun, Data Direct Networks (co-author, collaborator).
Lee Ward, Sandia National Laboratories (co-author, collaborator).

%\subsection*{Graduate and Postdoctoral Advisors and Advisees}
%{\bf List the names and current or- ganizational affiliations of your graduate advisor(s) and principal postdoctoral spon- sor(s). Also, list the names and current organizational affiliations of your graduate students and postdoctoral associates.}

\end{document}
